Paper Visualization

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
saving work

# Theme Prevelance Hypothesis

>>>>

# Theme Prevelance Hypothesis
```{r}
library(topicmodels)
library(tm)
library(SnowballC)
library(tidytext)
library(dplyr)
library(ggplot2)
library(igraph)
library(ggraph)

# Load the datasets
all_comments <- read.csv("/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/aids_related_comments_82TO86.csv")

# Data preparation: Select relevant text data
comments_corpus <- Corpus(VectorSource(all_comments$Content)) # Replace 'Content' with the actual column name containing text data

# Text preprocessing
comments_corpus <- comments_corpus %>%
  tm_map(content_transformer(tolower)) %>%  # Convert text to lowercase
  tm_map(removePunctuation) %>%              # Remove punctuation
  tm_map(removeNumbers) %>%                  # Remove numbers
  tm_map(removeWords, stopwords("english")) %>%  # Remove common stop words
  tm_map(stemDocument) %>%                   # Perform stemming
  tm_map(stripWhitespace)                    # Strip whitespace

# Create Document-Term Matrix (DTM)
dtm <- DocumentTermMatrix(comments_corpus)

# Remove sparse terms to reduce the size of DTM
dtm <- removeSparseTerms(dtm, 0.99) # Adjust sparsity threshold if necessary

# Check for rows with all zero entries and remove them
row_totals <- apply(dtm, 1, sum)
dtm <- dtm[row_totals > 0, ]

# Run LDA model to find themes (adjust number of topics as needed)
set.seed(123) # Set seed for reproducibility
lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed

# Display the top terms for each topic
top_terms <- terms(lda_model, 10)
print(top_terms)

# Visualize the top terms for each topic (concise visualization)
top_terms_df <- tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

# Plotting the top terms for each topic
ggplot(top_terms_df, aes(reorder_within(term, beta, topic), beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top Terms in Each Topic", x = "Term", y = "Beta") +
  theme_minimal()

# Co-occurrence Network Analysis
# Create a co-occurrence matrix
term_matrix <- as.matrix(dtm)
co_occurrence <- crossprod(term_matrix)

# Build graph object
graph <- graph_from_adjacency_matrix(co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
V(graph)$name <- colnames(co_occurrence)

# Simplify graph (remove loops and multiple edges)
graph <- simplify(graph)

# Visualize co-occurrence network
set.seed(123)
ggraph(graph, layout = 'fr') + 
  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE) + 
  geom_node_point(color = "blue", size = 5) + 
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void() +
  labs(title = "Co-occurrence Network of Themes")
```
